My Master thesis

### 2020-02-04 manuscript/drafts/manuscript.Rmd
a lot of stuff: fix bugs add bookdown

```{r}
# configurations table 
tab <- lapply(params, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("configurations")
```

```{r}

# combinations table
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

@@

```{r}
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  footnote(general = "nb model only works with tfidf feature extraction strategy. " )
```

>>>>

```{r}
# configurations table 
tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("Configurations")

```

```{r}
# combinations table
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

@@

```{r}
names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) 
```

### 2020-02-04 manuscript/index/05-appendix.Rmd
a lot of stuff: fix bugs add bookdown

---
title: "Definition list"
author: "Gerbrich Ferdinands"
date: "1/20/2020"
output: pdf_document
---

Model.

@@

        { some code, part of Definition 2 }

@@

Query Strategy
:   def

        { some code, part of Definition 2 }

        add paragraph here

    Uncertainty sampling.
    :  Selects the least sure instances for labelling.

    Maximum sampling.
    :  Selects the samples with the highest prediction probability.

@@

        { some code, part of Definition x }

@@

>>>>

`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

<!--
If you feel it necessary to include an appendix, it goes here.
-->

# List of Definitions
Model.

@@

        some code, part of Definition 2

@@

Query Strategy 
:   The way papers are queried to the researcher

        query_strategy

    Uncertainty sampling
    :  Selects the least sure instances for labelling.

    Maximum sampling
    :  Selects the samples with the highest prediction probability.

@@

        feature_extraction

@@

<!-- # The Last Appendix -->

<!-- This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup. -->

<!-- **In the main Rmd file** -->

<!-- ```{r ref.label='include_packages', results='hide', echo = TRUE} -->
<!-- ``` -->

<!-- **In Chapter \@ref(ref-labels):** -->

<!-- ```{r ref.label='include_packages_2', results='hide', echo = TRUE} -->
<!-- ``` -->
